%-------------------------
% Resume in Latex
% Author : Tyler McGraw
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

\input{glyphtounicode}

\pagestyle{empty}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeSummary}[1]{
  \small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Tyler McGraw} \\ \vspace{5pt}
    \href{mailto:tyler.a.mcgraw@gmail.com}{\underline{tyler.a.mcgraw@gmail.com}} $|$ \href{https://linkedin.com/in/tylermcgraw}{\underline{linkedin.com/in/tylermcgraw}} $|$ \href{https://github.com/tylermcgraw}{\underline{github.com/tylermcgraw}} $|$ \small San Francisco Bay Area, CA \\ \vspace{1pt}
\end{center}

I am a full-stack software engineer with several years of experience in the JavaScript and Python ecosystems. I recently co-created \emph{\href{https://chunkwise.github.io/}{\underline{Chunkwise}}}, an open-source, self-managed platform that evaluates chunking strategies and deploys ETL pipelines for RAG systems.

%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
        {\textbf{Co-Creator and Software Engineer} $|$ \emph{Chunkwise}}{2025 -- Present}
            \resumeItemListStart
                \resumeItem{Scaled the ETL pipeline to parallelize document processing while managing external API rate limits to prevent throttling. \emph{(AWS Batch (Fargate), OpenAI API)}}
                \resumeItem{Developed a real-time job tracking system to stream progress from AWS Batch document processing jobs to the client UI. \emph{(Server-sent events (SSE))}}
                \resumeItem{Built a web interface for experimentation via real-time visualization, side-by-side metrics comparison, and one-click deployment of validated strategies to production. \emph{(TypeScript, React)}}
                \resumeItem{Developed a modular backend using shared Pydantic models across chunking, evaluation, and orchestration services. \emph{(Python, FastAPI, Docker, ECR)}}
                \resumeItem{Created a uniform abstraction layer over multiple third-party chunking libraries, enabling consistent visualization and evaluation. \emph{(LangChain, Chonkie)}}
                \resumeItem{Built an evaluation service that calculates Precision, Recall, and IoU metrics, giving users a quantitative way to measure how chunking strategies impact retrieval accuracy. \emph{(ChromaDB, OpenAI API)}}
                \resumeItem{Designed a RESTful API to persist workflow data, orchestrate services, and coordinate AWS Batch jobs. \emph{(FastAPI)}}
                \resumeItem{Managed data persistence for LLM queries, embeddings, and workflows. \emph{(Amazon RDS PostgreSQL, pgvector, Amazon S3)}}
                \resumeItem{Authored a technical \href{https://chunkwise.github.io/case_study/overview/}{\underline{case study}} and built a professional website. \emph{(TypeScript, Astro)}}
            \resumeItemListEnd
        \resumeSubheading
            {\textbf{Software Engineer} $|$ \emph{Open Source Projects}}{2024 -- 2025}
            \resumeItemListStart
                \resumeItem{Request Bin: A developer tool for receiving, persisting, and inspecting HTTP requests and webhooks via a generated URL endpoint \emph{(JavaScript, Express, MongoDB, PostgreSQL, WebSockets, AWS, Nginx)}}
                \resumeItem{Job Hunt Assistant: A RAG application with chat history and token management \emph{(Python, PostgreSQL, RAG)}}
                \resumeItem{Shopping Cart: An e-commerce shopping cart app \emph{(TypeScript, React, Express, MongoDB)}}
            \resumeItemListEnd
        \resumeSubheading
            {\textbf{High School Mathematics Teacher}}{2023 -- 2025}
            \resumeItemListStart
                \resumeItem{Taught AP Computer Science Principles, AP Calculus, AP Statistics, AP Precalculus, and Precalculus Honors}
                \resumeItem{Founded three new AP courses, a math competition team, and a D\&D club}
                \resumeItem{Led AI initiatives for students and teachers including guest speakers and workshops}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Skills}
    \resumeSubHeadingListStart
        \resumeSubheading
        {\textbf{Languages}: TypeScript, Python, SQL, HTML, CSS}{}
        \resumeSubheading
        {\textbf{Frameworks}: Node.js, React, Express, FastAPI, Flask}{}
        \resumeSubheading
        {\textbf{AI}: OpenAI API, LangChain and Chonkie libraries, Context Engineering, RAG, Vector Databases, Embeddings}{}
        \resumeSubheading
        {\textbf{Cloud}: AWS (ECS, EC2, Lambda, Batch, RDS, S3, Secrets Manager, CDK, CLI), DigitalOcean, Heroku}{}
        \resumeSubheading
        {\textbf{Other}: PostgreSQL, SQLite, MongoDB, Jest, Vitest, Pytest, Git, Docker, RESTful APIs, Linux, Nginx}{}
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {\textbf{Washington University in St. Louis}}{2016 -- 2020}
            \resumeItemListStart
                \resumeItem{Bachelor of Arts in Philosophy-Neuroscience-Psychology, Minor in Computer Science}
                \resumeItem{Relevant Coursework: Data Structures and Algorithms, Object-Oriented Programming, Discrete Math}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}